Experiment 3 of 4

### 2016-07-28 experiments/e0/writeup/e0.Rmd
tidying up

---
title: "Experiment 0 pilot"
author: "Matt Green"
output:
  html_document:
    toc: yes
    mathjax: default
    template: default
    code_folding: hide
    theme: default
---

>>>>

---
title: "Experiment 0 pilot"
author: "Matt Green"
output:
  html_document:
    toc: yes
    <!--toc_float: true-->
    mathjax: default
    template: default
    code_folding: hide
    theme: default
---

### 2016-07-28 experiments/e1/writeup/e1.Rmd
tidying up

---
title: "Experiment 1 of 4"
output:
  html_document:
    toc: yes
    mathjax: default
    template: default
    code_folding: hide
    theme: default
---

@@

```{r sourceFunctions}
source("functions/CIfunctions.R")
```

>>>>

---
title: "Experiment 1 of 4"
author: "Matt Green"
output:
  html_document:
    toc: yes
    <!--toc_float: true-->
    mathjax: default
    template: default
    code_folding: hide
    theme: default
---

@@

```{r sourceFunctions}
source("CIfunctions.R")
```

### 2016-07-28 experiments/e2/writeup/main.Rmd
tidying up

---
title: "Experiment 2 of 4: main"
output:
  html_document:
    toc: true
    <!--toc_float: true-->
    mathjax: default
    template: default
    code_folding: hide
    theme: default
---

>>>>

---
title: "Experiment 2 of 4: main"
author: "Matt Green"
output:
  html_document:
    toc: true
    <!--toc_float: true-->
    mathjax: default
    template: default
    code_folding: hide
    theme: default
---

### 2016-07-28 experiments/e3/writeup/e3.Rmd
tidying up

---
title: "Experiment 3 of 4"
output:
  html_document:
    toc: true
    <!--toc_float: true-->
    mathjax: default
    template: default
    code_folding: hide
    theme: default
---  
# Experiment 3

@@

```{r readdata}
dat <- read.delim("data/allresults.txt", stringsAsFactors = FALSE)

@@

# save dat as dat.Rda
# This data set contains *all* trials including impossible trials and is mainly for graphs comparing different removals
save(dat, file="dat.Rda")

@@

# save dd as dd.Rda
# This data set non-impossible trials and renamed/recomputed variables
save(dd, file="dd.Rda")
```

@@

```{r boxplot subjects and items}
load("dd.Rda")
# allow reference to transformation
subdata = melt(dd,
               measure.vars=c("RT_Rec", "RT_RecSqt", "RT_log", "RT_raw"),
               variable.name="transformation",
               value.name="value") 
# boxplots for subjects and items separately for each dependent variable
ggplot(subdata) + 
  facet_wrap(~ variable, scales="free", ncol=4) +
  geom_boxplot(aes(y=value, x=Item, col="Items")) + 
  geom_boxplot(aes(y=value, x=Subject, col="Subjects")) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), aspect.ratio=1, panel.grid=element_blank()) + 
  scale_colour_manual("",values=c("Items"="red","Subjects"="blue")) +
  xlab("") + ylab("")
```

```{r load_dd}
load("dd.Rda")
```

@@

```{r coeff}
par(las=2, mar=c(14,6,1,1))
y=as.data.frame(summary(v5)$coef[-1,1]) # estimates, without intercept
q=confint(v5)[-c(1,2,3),]
y=cbind(y,q)
plot(y[,1], ylim=range(y[,1],y[,2],y[,3]), xaxt="n", xlab="", ylab="estimate\n",  pch='-', cex=2)
segments(x0=1:nrow(y), x1=1:nrow(y), y[,2], y[,3])
abline(h=0)
axis(1, labels=row.names(y), at=1:nrow(y), srt=45)
grid()
```

@@

par(mfrow=c(1,4), pty='s')
# create scaled residuals
v5$rstand = as.vector(scale(resid(v5)))
# plot scaled residuals density
plot(density(v5$rstand))
# plot sample quantiles versus theoretical quantiles
qqnorm(v5$rstand, cex=.5)
qqline(v5$rstand)
# plot standardised residuals versus fitted values
plot(v5$rstand ~ fitted(v5), pch='.')
# absolute standardised residuals greater than 2.5 are candidates for being outliers, the abline identifies them on the plot
abline(h=c(-2.5,2.5))
# create dffits
dffits=abs(resid(v5, "dffits"))
# plot dffits
plot(dffits, type='h')
```

>>>>

---
title: "Experiment 3 of 4"
author: "Matt Green"
output:
  html_document:
    toc: true
    <!--toc_float: true-->
    mathjax: default
    template: default
    code_folding: hide
    theme: default
---

# Experiment 3

@@

```{r readdata}
dat <- read.delim("allresults.txt", stringsAsFactors = FALSE)

@@

# The dat data set contains *all* trials including impossible trials 
# and is mainly for graphs comparing different removals

@@

# save dd as data.Rda
# This data set non-impossible trials and renamed/recomputed variables
save(dd, file="data.Rda")
```

@@

```{r boxplot subjects and items}
load("data.Rda")
# allow reference to transformation
subdata = melt(dd,
               measure.vars=c("RT_Rec", "RT_RecSqt", "RT_log", "RT_raw"),
               variable.name="transformation",
               value.name="value") 
# boxplots for subjects and items separately for each dependent variable
ggplot(subdata) + 
  facet_wrap(~ variable, scales="free", ncol=4) +
  geom_boxplot(aes(y=value, x=Item, col="Items")) + 
  geom_boxplot(aes(y=value, x=Subject, col="Subjects")) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), aspect.ratio=1, panel.grid=element_blank()) + 
  scale_colour_manual("",values=c("Items"="red","Subjects"="blue")) +
  xlab("") + ylab("")
```

@@

```{r coeff}
v5 <- lme4::lmer(data=dd, 
           RT_RecSqt ~ 
             c_Vag + Selection.sum + c_Qty + c_Ord + 
             Selection.sum:c_Vag:c_Qty +
             item_mean_ratio + 
             s_Trl +
             RTprev_RecSqt +
             nchar_instr +
             (1+c_Vag + Selection.sum + c_Qty + c_Ord|Subject)
)
par(las=2, mar=c(6,6,1,1))
y=data.frame(coef=summary(v5)$coef[-1,1]) # estimates, without intercept
q=confint(v5, method="Wald")[-c(1,2,3),]
y=cbind(y,q[15:23,])
plot(y[,1], ylim=range(y[,1],y[,2],y[,3]), xaxt="n", xlab="", ylab="estimate\n",  pch='-', cex=2)
segments(x0=1:nrow(y), x1=1:nrow(y), y[,2], y[,3])
abline(h=0)
axis(1, labels = abbreviate(row.names(y), minlength=10), , at=1:nrow(y), las=2)
grid()
```

@@

par(mfrow=c(1,4), pty='s')
# create scaled residuals
dd$rstand = as.vector(scale(resid(v5)))
# plot scaled residuals density
plot(density(dd$rstand))
# plot sample quantiles versus theoretical quantiles
qqnorm(dd$rstand, cex=.5)
qqline(dd$rstand)
# plot standardised residuals versus fitted values
plot(dd$rstand ~ fitted(v5), pch='.')
# absolute standardised residuals greater than 2.5 are candidates for being outliers, the abline identifies them on the plot
abline(h=c(-2.5,2.5))
# create dffits
#dffits=abs(resid(v5, "dffits"))
# plot dffits
#plot(dffits, type='h')
```
